Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-18 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex
First typo-correction

In a study investigating the formation of human immunodeficiency virus-like
particles (VLPs) the correlated SICM-fluorescence confocal microscopy was used
to investigate topography changes together with die distribution of
fluorescently labeled viral proteins like Gag or Viral Protein R
\cite{Bednarska2020}. In contrast to investigating the virus formation with
TIRF microscopy \cite{Jouvenet2008}, the combination of SICM and confocal FM
allowed to investigate the apical side of the cells. It was found that the
release of VLPs is a lot faster than the release at the basal cell side as
known from TIRF investigations and furthermore, a potential impact on the
release time by the application of a fluorescent marker was found
\cite{Bednarska2020}.

@@

In both setups, an SICM is mounted onto an inverted confocal microscope and
before simultaneous recording, the focus of the confocal FM objective is
aligned with the tip of the SICM probe via micrometer screws and the confocal
microscope's focusing mechanics. The
difference between the two setups is the way how the SICM pipette, the
confocal focus and the sample are positioned with respect to each other during
imaging. The
first setup (Fig.~\ref{fig:sscm_setup}a) keeps the 
SICM probe at a fixed position and scanning is performed by the sample
stage which positions the sample in all three dimensions.

@@

\begin{figure}
  \centering
  \includegraphics{gr/correlating/SSCM-np}
  \caption{%
    \textbf{Investigation on nanoparticle uptake by SSCM.}  \textbf{a:} Height
    profile of a section of a AT1-like cell treated with 200\,nm fluorescent
    nanoparticles.  \textbf{b:} Slope representation of the area shown in a.
    \textbf{c:} Surface fluoresecence of the same area.  \textbf{d:} Overlay
    of surface fluorescence and slope representation.  Yellow arrowheads mark
    nanoparticles that co-localise with membrane protrusions (white
    arrowheads), blue arrowheads mark nanoparticles being in the process of
    internalisation, green arrowheads mark fully internalised nanoparticles.
    Reprinted with permission from P. Novak, A Shevchuk, P. Ruenraroengsak, et
    al.: \emph{Imaging Single Nanoparticle Interactions with Human Lung Cells
      Using Fast Ion Conductance Microscopy.} Nano Lett. 2014, 14, 3,
    1202–1207. Copyright 2014 American Chemical Society.}
  \label{fig:sscm-np}
\end{figure}

>>>>

In a study investigating the formation of human immunodeficiency virus-like
particles (VLPs) the correlated SICM-fluorescence confocal microscopy was used
to investigate topography changes together with the distribution of
fluorescently labeled viral proteins like Gag or Viral Protein R
\cite{Bednarska2020}. In contrast to investigating the virus formation with
TIRF microscopy \cite{Jouvenet2008}, the combination of SICM and confocal FM
allowed to investigate the apical side of the cells. It was found that the
release of VLPs is a lot faster than the release at the basal cell side as
known from TIRF investigations and furthermore, a potential impact on the
release time by the application of a fluorescent marker was found
\cite{Bednarska2020}.

@@

In both setups, a SICM is mounted onto an inverted confocal microscope and
before simultaneous recording, the focus of the confocal FM objective is
aligned with the tip of the SICM probe via micrometer screws and the confocal
microscope's focusing mechanics. The
difference between the two setups is the way how the SICM pipette, the
confocal focus and the sample are positioned with respect to each other during
imaging. The
first setup (Fig.~\ref{fig:sscm_setup}a) keeps the 
SICM probe at a fixed position and scanning is performed by the sample
stage which positions the sample in all three dimensions.

@@

\begin{figure}
  \centering
  \includegraphics{gr/correlating/SSCM-np}
  \caption{%
    \textbf{Investigation on nanoparticle uptake by SSCM.}  \textbf{a:} Height
    profile of a section of a AT1-like cell treated with 200\,nm fluorescent
    nanoparticles.  \textbf{b:} Slope representation of the area shown in a.
    \textbf{c:} Surface fluorescence of the same area.  \textbf{d:} Overlay
    of surface fluorescence and slope representation. Yellow arrowheads mark
    nanoparticles that co-localise with membrane protrusions (white
    arrowheads), blue arrowheads mark nanoparticles being in the process of
    internalisation, green arrowheads mark fully internalised nanoparticles.
    Reprinted with permission from P. Novak, A Shevchuk, P. Ruenraroengsak, et
    al.: \emph{Imaging Single Nanoparticle Interactions with Human Lung Cells
      Using Fast Ion Conductance Microscopy.} Nano Lett. 2014, 14, 3,
    1202–1207. Copyright 2014 American Chemical Society.}
  \label{fig:sscm-np}
\end{figure}
